Running faster scripts with DaemonMode.jl

### 2021-10-15 paper/paper.tex
Avoid symbol with problems in UTF-8.

The output is nice:
\begin{lstlisting}
$ jclient test_log1.jl
  ┌ Warning: warning 1
  │ another line
  │ last one
  └ @ Main /.../test_log1.jl: 4
  ┌ Error: error 1
  └ @ Main /.../test_log1.jl: 5
  ┌ Info: info 1
  └ @ Main /.../test_log1.jl: 6
\end{lstlisting}

>>>>

The output is nice:
\begin{lstlisting}
$ jclient test_log1.jl
   Warning: warning 1
   another line
   last one
   @ Main /.../test_log1.jl: 4
   Error: error 1
   @ Main /.../test_log1.jl: 5
   Info: info 1
   @ Main /.../test_log1.jl: 6
\end{lstlisting}
